The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-04-12 docs/language_constraint_emnlp.tex
EMNLP submitted version

\begin{table}[!t]
\small
%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
%\begin{tabular}{|p{4.8cm}|p{1.9cm}|} \hline
\begin{tabularx}{\linewidth}%
{l>{\setlength\hsize{0.67\hsize}}X%
>{\setlength\hsize{1.33\hsize}}X}
{\bf Story Prefix} & {\bf Ending} \\ \hline
\multirow{4}{*}{\parbox{4.75cm}{%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
\vspace{.1cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it \tiny $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
& 	{\color{forestgreen}{\vspace{-0.1cm}She was full and happy.     %Then he got hired.
}} \\ \cline{2-2}
& {\color{red}{%Joe hated pizza.
\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.}} \\\hline %\cline{2-2}
%&  \\ \hline
\end{tabularx}
\caption{\label{ROC-example}
Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
 %of the same story: 
The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story. Unfortunately Nasrin et al.  didn't publish the original endings for the dev/test data. We could ask her, but not sure if this is worth it}}
 \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
let's consider just color-coding these three terms.  It's less distracting.}}
}
%\end{center}
\end{table}

@@

\paragraph{Combination with a neural language model.}
We investigate whether our model can benefit from state-of-the-art text comprehension models\shortv{, for which this task was designed}. 
We experiment with an LSTM \cite{hochreiter1997long} recurrent neural network language model (LM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
Unlike the model in this paper\shortv{, which only considers the story endings}, this LM \shortv{follows the protocol suggested by the story cloze task designers, and }harnesses the story cloze training set, which consists of single-ending stories, 
as well as the story context for each pair of endings.\footnote{The LM training details are in the supplementary file.} 
We show that adding our features to this powerful LM
gives improvements over our classifier as well as the LM.\resolved{\nascomment{reworded.  more important that our features help
  the language model, than the other way around!}}\supl{
\shortv{We train the RNNLM using a single-layer LSTM of hidden dimension 512.}
\shortv{We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model.}\shortv{We replace all words occurring less than 3 times with a special
out-of-vocabulary character, yielding a vocabulary size of  21,582.
Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. }
We train the RNNLM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
$\eta=.001$, while minimizing cross-entropy.} % minibatches of $50$ stories.
% h=512, dropout rate of 60%, V=21582, 10% validation set
To apply it to the classification problem, we select
as \emph{right} the ending with the higher value of\shortv{\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
the model)
given the four preceding sentences of the story (the numerator), controlling for the
inherent surprisingness of the words in that ending (the denominator).}}
\begin{equation}
\frac{p_\theta(\textrm{ending} \mid
  \textrm{story})}{p_\theta(\textrm{ending})} \label{eq:ratio}
\end{equation}
\roy{Selecting endings based on the ratio in Equation~\ref{eq:ratio} achieves 67.7\% on the story cloze task\shortv{ (see
\tabref{cloze_results})}.}

>>>>

\begin{table}[!t]
\small
%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
%\begin{tabular}{|p{4.8cm}|p{1.9cm}|} \hline
\begin{tabularx}{\linewidth}%
{l>{\setlength\hsize{0.67\hsize}}X%
>{\setlength\hsize{1.33\hsize}}X}
{\bf Story Prefix} & {\bf Ending} \\ \hline
\multirow{4}{*}{\parbox{3.05cm}{\vspace{.05cm}John liked a girl at his work.	He tried to get her attention by acting silly.	She told him to grow up. John confesses he was trying to make her like him more.}} & \vspace{-0.2cm}	{\color{blue}{{She feels flattered and asks John on a date.}}} 	 \\\cline{2-2}

%Travis needed some fast cash.	He thought about it and decided that selling his car was a good idea.	Travis listed his car for sale in the local paper.	After only a couple weeks he found somebody very interested.}}& \vspace{-0.2cm}	{\color{blue}{{\it This person came and test drove the car and bought it on the spot.}}} \\\cline{2-2}
%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
%\vspace{.3cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.% He sold the car and solved his money problems.%She was full and happy.     %Then he got hired.
}} \\ \cline{2-2}
& {\color{red}{%Joe hated pizza.\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.
\vspace{-0.1cm}John was happy about being rejected.%Travis gave it to the man for free.
}} \\\hline %\cline{2-2}
%&  \\ \hline
\end{tabularx}
\caption{\label{ROC-example}
Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
 %of the same story: 
The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story. Unfortunately Nasrin et al.  didn't publish the original endings for the dev/test data. We could ask her, but not sure if this is worth it}}
 \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
let's consider just color-coding these three terms.  It's less distracting.}}
}
%\end{center}
\end{table}

@@

\paragraph{Combination with a neural language model.}
We investigate whether our model can benefit from state-of-the-art text comprehension models\shortv{, for which this task was designed}. 
We experiment with an LSTM \cite{hochreiter1997long} recurrent neural network language model (LM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
Unlike the model in this paper\shortv{, which only considers the story endings}, this LM \shortv{follows the protocol suggested by the story cloze task designers, and }harnesses the story cloze training set, which consists of single-ending stories, 
as well as the story context for each pair of endings.\footnote{The LM training details are in the supplementary file.} 
We show that adding our features to this powerful LM
gives improvements over our classifier as well as the LM.\resolved{\nascomment{reworded.  more important that our features help
  the language model, than the other way around!}}\supl{
\shortv{We train the RNNLM using a single-layer LSTM of hidden dimension 512.}
\shortv{We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model.}\shortv{We replace all words occurring less than 3 times with a special
out-of-vocabulary character, yielding a vocabulary size of  21,582.
Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. }
We train the RNNLM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
$\eta=.001$, while minimizing cross-entropy.} % minibatches of $50$ stories.
% h=512, dropout rate of 60%, V=21582, 10% validation set
To apply this LM to the classification problem, we select
as \emph{right} the ending with the higher value of\shortv{\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
the model)
given the four preceding sentences of the story (the numerator), controlling for the
inherent surprisingness of the words in that ending (the denominator).}}
\begin{equation}
\frac{p_\theta(\textrm{ending} \mid
  \textrm{story})}{p_\theta(\textrm{ending})} \label{eq:ratio}
\end{equation}
\roy{Selecting endings based on the ratio in Equation~\ref{eq:ratio} achieves 67.7\% on the story cloze task\shortv{ (see
\tabref{cloze_results})}.}
